---
title: "Using the UWBiost561 package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the UWBiost561 package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This document introduces to you how to use the package **UWBiost561** for graph generation and finding the maximal partial clique.

We first use the generate_partial_clique() function to generate an adjacency matrix with a dense subgraph.
```{r}
library(UWBiost561)
set.seed(42)
gen_result <- generate_partial_clique(n = 10, clique_fraction = 0.5, clique_edge_density = 0.8)
adj_mat <- gen_result$adj_mat

print(adj_mat)
```

We visualize the graph to inspect its structure.

```{r}
library(igraph)

g <- graph_from_adjacency_matrix(adj_mat, mode = "undirected", diag = FALSE)
plot(g, vertex.label = NA, vertex.size = 20,
     main = "Random Partial Clique (10 nodes)")
```

Next, we use the `compute_maximal_partial_clique()` function to find a dense subgraph that exceeds a given edge density threshold.

```{r}
result <- compute_maximal_partial_clique(adj_mat, alpha = 0.7, verbose = TRUE)

cat("Nodes in maximal partial clique:", result$clique_idx, "\n")
cat("Edge density of clique:", round(result$edge_density, 3), "\n")
```

We now run a small-scale simulation to evaluate different implementations of computing the maximal partial clique on graphs of varying sizes and density thresholds.

```{r}
n_vec <- c(10, 12)          # small sizes for speed
alpha_vec <- c(0.6, 0.8)    # varying thresholds

# Simulate using implementations 1 and 2 only
results <- perform_simulation(
  imp_numbers = 1:10,
  trials = 2,
  n_vec = n_vec,
  alpha_vec = alpha_vec
)

# Print result structure
str(results)
```